---
title: "Automated Item Generation Using GPT-3"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, python.reticulate = FALSE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{python, eval = FALSE}
import os
import openai

openai.api_key = os.getenv("OPENAI_API_KEY")

response = openai.Completion.create(
  engine="davinci",
  prompt="Objective: This program generates items that measure Big Five personality traits.\n\ntrait: neuroticism\nnumber of items to generate: 6\n1. I dislike myself .\n2. I am someone who stays optimistic after experiencing a setback .\n3. I panic easily .\n4. I suspect that my facial expressions give me away when I feel sad .\n5. I am not easily bothered by things .\n6. I seldom feel blue .\n###\ntrait: openness\nnumber of item to generate: 4\n1. Others perceive that I do not have original ideas, and I am not inventive .\n2. I have a vivid imagination .\n3. I am someone who avoids intellectual philosophical discussions .\n4. I do not enjoy watching dance performances .\n###\ntrait: agreeableness\nnumber of items to generate: 2\n1. I become frustrated and angry with people when they don't live up to my expectations .\n2. When interacting with a group of people, am often bothered by at least one of them .\n###\ntrait: extraversion\nnumber of items to generate: 10\n1. I am often accused of being self-centered .\n2. I can talk to many different types of people without feeling uncomfortable .\n3. I do not like to draw attention to myself in social situations .\n4. When in a group, I tend to be the center of attention .\n5. People consider me an authority on fashion and style .\n6. I am not comfortable around people unless they are doing what I want them to do .\n7. In a conversation, I tend to focus my attention on the person who is speaking at that moment .\n8. People often ask for my advice about how they should behave in certain social situations .\n9. In a meeting, it is easy for me to get distracted by what other people are saying or doing .\n10. I love parties and social events where there are lots of other people present .",
  temperature=0.7,
  max_tokens=200,
  top_p=0.9,
  frequency_penalty=0.5,
  presence_penalty=0.5,
  stop=["###"]
)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
